### 2019-04-08 2-Chapters/5-Chapter/chapter5.tex
Done
Expérience en cours pour la fin du Chapitre:3.

FIXME Je dois refaire ces simulations, les chiffres ici sont avec $T=1000$ et $N=4$ répétitions (juste faites vite fait dans le train, je dois les lancer sur la machine du bureau).
}

\begin{table}[ht]
    % \begin{footnotesize}
        \centering
        \begin{tabular}{c|ccc}
        \textbf{Algorithms} $\;$ \textbackslash $\;$ \textbf{Number of players} & $M=3$ & $M=6$ & $M=9$ \\
            \hline
            Centralized multiple-play \klUCB{} & $\mathbf{52 \pm 15}$ & $\mathbf{35 \pm 15}$ & $\mathbf{0}$ \\
            \hline
            \RhoRand-\klUCB{} & $297 \pm 18$ & $1411 \pm 144$ & $2351 \pm 55$ \\
            \RhoRand-\klUCB{} + \textcolor{red}{Estimate $M$} & \textcolor{red}{$326 \pm 86$} & \textcolor{red}{$1213 \pm 168$} & \textcolor{red}{$2403 \pm 121$} \\
            \hline
            \RandTopM-\klUCB{} & $188 \pm 18$ & $671 \pm 159$ & $790 \pm 470$ \\
            \RandTopM-\klUCB{} + \textcolor{red}{Estimate $M$} & \textcolor{red}{$238 \pm 27$} & \textcolor{red}{$778 \pm 156$} & \textcolor{red}{$1098 \pm 153$} \\
            \hline
            \MCTopM-\klUCB{} & $134 \pm 6$ & $304 \pm 19$ & $42 \pm 5$ \\
            \MCTopM-\klUCB{} + \textcolor{red}{Estimate $M$} & \textcolor{red}{$210 \pm 66$} & \textcolor{red}{$465 \pm 39$} & \textcolor{red}{$602 \pm 54$} \\
            \hline
            \Selfish-\klUCB{} & $136 \pm 17$ & $468 \pm 87$ & $1379 \pm 16$ \\
            \hline
        \end{tabular}
        \caption{Mean regret $\pm$ $1$ std-dev, for different algorithms on the same problem with $M=3,6,9$, comparing algorithms which knows $M$ against algorithms which estimate $M$ on the fly. The three algorithms \RhoRand, \RandTopM{} and \MCTopM{} all suffer from similar costs on their regret when they have to estimate $M$ on the fly. Our proposals are still much more efficient than \RhoRand{} when using the procedure to estimate $M$ described from \cite{Anandkumar11}.}
        \label{table:5:meanRegretSimulationsEstimatingM}
    % \end{footnotesize}
    \end{table}

>>>>

FIXME Je dois refaire ces simulations, les chiffres ici sont avec $T=1000$ et $N=4$ répétitions (juste faites vite fait dans le train, je dois les lancer sur la machine du bureau).

% for M in 3 6 9; do DEBUG=False SAVEALL=True NOPLOTS=True M=$M K=9 N_JOBS=-1 N=100 T=10000 make moremultiplayers; read; done
}

\begin{table}[ht]
% \begin{footnotesize}
    \centering
    \begin{tabular}{c|ccc}
    \textbf{Algorithms} $\;$ \textbackslash $\;$ \textbf{Number of players} & $M=3$ & $M=6$ & $M=9$ \\
        \hline
        Centralized multiple-play \klUCB{} & $\mathbf{52 \pm 15}$ & $\mathbf{35 \pm 15}$ & $\mathbf{0}$ \\
        \hline
        \RhoRand-\klUCB{} & $297 \pm 18$ & $1411 \pm 144$ & $2351 \pm 55$ \\
        \RhoRand-\klUCB{} + \textcolor{red}{Estimate $M$} & \textcolor{red}{$326 \pm 86$} & \textcolor{red}{$1213 \pm 168$} & \textcolor{red}{$2403 \pm 121$} \\
        \hline
        \RandTopM-\klUCB{} & $188 \pm 18$ & $671 \pm 159$ & $790 \pm 470$ \\
        \RandTopM-\klUCB{} + \textcolor{red}{Estimate $M$} & \textcolor{red}{$238 \pm 27$} & \textcolor{red}{$778 \pm 156$} & \textcolor{red}{$1098 \pm 153$} \\
        \hline
        \MCTopM-\klUCB{} & $134 \pm 6$ & $304 \pm 19$ & $42 \pm 5$ \\
        \MCTopM-\klUCB{} + \textcolor{red}{Estimate $M$} & \textcolor{red}{$210 \pm 66$} & \textcolor{red}{$465 \pm 39$} & \textcolor{red}{$602 \pm 54$} \\
        \hline
        \Selfish-\klUCB{} & $136 \pm 17$ & $468 \pm 87$ & $1379 \pm 16$ \\
        \hline
    \end{tabular}
    \caption{Mean regret $\pm$ $1$ std-dev, for different algorithms on the same problem with $M=3,6,9$, comparing algorithms which knows $M$ against algorithms which estimate $M$ on the fly.}
    \label{table:5:meanRegretSimulationsEstimatingM}
% \end{footnotesize}
\end{table}

\TODOL{Give interpretation from these results!}
One can observe in Table~\ref{table:5:meanRegretSimulationsEstimatingM} the empirical performances of different algorithms in an example problem, in each case of low, medium and maximum number of players ($M=3,6,9$ for $K=9$ arms).
The three algorithms \RhoRand, \RandTopM{} and \MCTopM{} all suffer from similar costs on their regret when they have to estimate $M$ on the fly. Our proposals are still much more efficient than \RhoRand{} when using the procedure to estimate $M$ described from \cite{Anandkumar11}.
For the two non-extreme cases ($M=3,6$), the performance drop when having to estimate $M$ is quite large (on the three algorithms and two cases, about $+30\%$), and consistent on the different algorithm.
The extreme case of $M=K$ players is of highest interest, as \MCTopM{} achieves a very small regret (proved to be $\smallO{\log(T)}$ as it is just the expected time of the orthogonalization process), while the same algorithm with unknown $M$ suffers from a much larger regret (written ``Estimate $M$'' in Table~\ref{table:5:meanRegretSimulationsEstimatingM}).
In this extreme case, \RhoRand{} and its extension both perform very closely, as expected.
